Table compiler

### 2017-12-06 analyses/table-compiler.Rmd
Fixed details of table 1

```{r}
## Getting the data
slugs <- list("Beck2014", "Brusatte2014", "Bapst2016", "bears", "Wright2017")

@@

## Trees lists
trees <- lapply(slugs, function(slug) read.nexus(paste0("../data/processed/tree.", slug, ".tre")))
## Adding Wright's tree age
trees[[5]]$root.time <- 485.4
```

@@

```{r}
## Column names
colnames <- c("Group", "n taxa", "m characters", "Age range", "Reference", "Notes")

@@

## Groups
group <- c("Eutherian mammals", "theropods", "theropods", "bears", "crinoids")

@@

## References and Notes (to be filled in LaTeX)
reference <- notes <- rep("", length(slugs))
notes[2] <- "2 + 9 taxa removed"
notes[3] <- "12 + 19 taxa removed. Tree was randomly selected from all time-scaled trees"
notes[4] <- "12 + 0 taxa removed"
notes[5] <-  "Maximum clade credibility tree, time-scaled by dividing branches by 0.03517385 and setting root time to 485.4"

## Formatting the table
table_out <- data.frame(group, ntaxa, mcharacters, age_ranges, reference, notes)
colnames(table_out) <- colnames
rownames(table_out) <- dataset

>>>>

```{r}
## Getting the data
slugs <- list("Beck2014", "Brusatte2014", "Bapst2016", "Wright2017")

@@

## Trees lists
trees <- lapply(slugs, function(slug) read.nexus(paste0("../data/processed/tree.", slug, ".tre")))
## Adding Wright's tree age
trees[[4]]$root.time <- 485.4
```

@@

```{r}
## Column names
colnames <- c("Group", "# taxa", "# characters", "Age range (MYA)", "Mass extinction (MYA)", "Reference(s)")

@@

## Groups
group <- c("eutherian mammals", "theropods", "theropods", "crinoids")

@@

## Mass extinction
mass <- c("66", "66", "66", "443")

## References (to be filled in LaTeX)
reference <- rep("", length(slugs))

## Formatting the table
table_out <- data.frame(group, ntaxa, mcharacters, age_ranges, mass, reference)
colnames(table_out) <- colnames
rownames(table_out) <- dataset
